---
title: "BF HW-5"
author: "ta560@scarletmail.rutgers.edu"
date: "10/13/2022"
output: html_document
---
  
## Decompose
  
* Data Set - usmelec

```{r}
library(fpp)
library(fpp2)

head(usmelec)
plot(usmelec)
stl_decomp <- stl(usmelec,s.window ="periodic")
plot(stl_decomp)
attributes(stl_decomp)
```

* The function decompose is used to break the data into components that is trend, seasonality and the irregularity.
* From the above plot, we can see that there is a seasonality in the data and and an upward trend as well.
* The irregularity component gradually increases through the period.

```{r}
seasadj(stl_decomp)

plot(usmelec)
lines(seasadj(stl_decomp), col="Red")
```

* The function seasadj adjusts the seasonality of the data and gives the data without the seasonal component.
* The plot above shows the data without seasonal component in red color. 

```{r}
f_stl <- forecast(stl_decomp,h=15)
f_stl
plot(f_stl)
```

* The f_stl above is forecasting the data. the "h" mentioned is the time period for which we need the forecast. 
* In the plot, the dark and light gray area is the 85% and 95% confidence interval of the forecast respectively.

```{r}
f_stl2 <- forecast(stl_decomp,h=50)
plot(f_stl2)
```

* We have taken value of H as 100 to get a better understanding of the data.
* We can see that when the time period increases the confidence interval also increases.
* The forecast gets poorer we try to forcast it for longer period.

## lets try a different way to decompose

```{r}
decomp_usmelec <- decompose(usmelec)

attributes(decomp_usmelec)
seasadj(decomp_usmelec)
```

* decompose() function is another way we can use to decompose our data.
* In the attribute we can see that there are trend, seasonal, and random variables.
* seasadj also is useful to adjust the seasonal variation as the decompose() function.

```{r}
plot(decomp_usmelec)
```

* The order of trend, seasonal, and irregularity changes while the visual remains the same.
* "random" is used to show the irregularity component and it is shown in the form of a line graph.
