---
title: "BFA6"
author: "ta560@scarletmail.rutgers.edu"
date: "11/14/2022"
output: html_document
---
  
```{r}
library(fpp)
library(fpp2)
library(forecast)
```

## Data set - usmelec (fpp)

#### plot of usmelec

```{r}
plot(usmelec, main = 'Monthly electricity generated in the US', xlab = 'Year', ylab = 'Electricity units')
```

* Trend and Seasonality can be seen in the plot.
* There is an increase of residuals when we perform all the tests which indicates that the latest data is different from the past data.
* So,lets consider a window of the data from 2000.

#### Window Plot

```{r}
usmelec_win <- window(usmelec, start = 2000)
plot(usmelec_win, main = 'Monthly electricity generated in the US', xlab = 'Year', ylab = 'Electricity generated')
```

* Even here, we can observe both trend and seasonality from the first glance.
* Lets do an Acf function.

#### Acf plot

```{r}
Acf(usmelec_win, main = 'Acf Plot - Usmelec from 2000')
```

* The Acf plot shows both trend and seasonality present in the plot.
* Since there is seasonality we use both nsdiffs and ndiffs.

## ARIMA for data with seasonal component

#### Checking the Differencing needed for seasonal component

```{r}
nsdiffs(usmelec_win) #nsdiffs is for seasonal
```

* nsdiffs is use to know how many differences we need to do for seasonality component.
* We first go ahead with seasonality beacuse most of the cases, ones we do this, trend takes care of itself.

#### Checking the Differences needed

```{r}
ndiffs(usmelec_win)
```

* We got ndiffs as 1 initially. 
* Let us first perform the differences for seasonal data and check ndiffs again.

#### Rechecking the differencing needed after performing the seasonal differencing

```{r}
ndiffs((diff(usmelec_win,12))) #12 because it is monthly
```

* As mentioned above, we can see that the ndiffs now becomes zero indicating that the trend component took care of itself.

#### Acf and Pacf plots

```{r}
tsdisplay(diff(usmelec_win,12))
```

* In the Acf plot we can see that the p value is 11.

#### Arima Model

```{r}
arima_fit <- auto.arima(usmelec_win,trace=TRUE, stepwise = FALSE )
arima_fit
```

* The system runs the auto arima and gives out the best model for which the AIC value is the lowest.AIC value is 1102.04 from the arima function.
* The model tested multiple p,q,P,Q values other than the ones we predicted earlier.

#### Arima Model attributes

```{r}
attributes(arima_fit)
```

#### Plot the forecast of the Arima model with confidence interval of 99% 

```{r}
plot(forecast(arima_fit,h=5,level=c(99)), main = 'Forecast of the ARIMA model', xlab = 'Year', ylab = 'Electricity Generated')
```

## Residual Analysis

#### Acf of Residuals

```{r}
Acf(arima_fit$residuals)
```

* We can see there is white noice in the acf plot.
* No data crosses the confidence interval line which tells us it is a good forecast.

#### Box-Ljung test

```{r}
Box.test(residuals(arima_fit), lag=20, type="Ljung")
```

* We got p-value 0.9666 which is greater than 0.05 means that the null hypothesis is true

#### Residuals plot

```{r}
plot.ts(residuals(arima_fit))
```

* The residuals look random and mean to be around zero.
* This means its a very good forecasting model.

#### Histogram plot of residuals

```{r}
hist(arima_fit$residuals)
```

* The histogram above shows residuals have a mean around zero.
* This distribution does not look like a perfect normal distribution.

#### TSDiagram of the ARIMA model

```{r}
tsdiag(arima_fit)
```

* The function tsdiag() shows the overall residual analysis plots together.
* The standardized residuals plot looks normal. Two of the residuals are very close to touch the z-score of 2.
* There is only 1 significant value in the Acf plot which crosses the confidence interval.
* We can see all the p-values in Ljung-Box test are above the confidence level, which means residuals are random.
* Overall, this ARIMA model seems a good fit.





